Random Forests", OAs

### 2023-11-24 src/oa_RF.Rmd
cast

library(tidyverse)
library(rprojroot)
library(rgdal)
library(rgeos)
library(sf)
library(spdep)
#library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
#library(foreach)
library(doParallel)
library(raster)
library(plm)
#library(lmtest)
library(caret)
library(randomForest)

@@

# out.path <- paste0(path, "/data/temp/oa_rf.RData")
# save.image(file = out.path)
# load(out.path)

@@

print(model.all)

@@

@@

@@

@@

regions <- df %>% distinct(RGN21CD)
regions <- as.vector(regions$RGN21CD)

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN21CD==i), 
                                spacevar = "oa11cd",
                                timevar = "year", 
                                k = 10)

  model.all <- train(n ~ area + dist + dist.retail + London + south + 
                     n.slag + n.lag + n.l.slag + n.nearest.city + year,
                   data = df %>% filter(RGN21CD==i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")
  assign(paste0("model.all",as.character(i)), model.all)
}

@@

@@

@@

  #assign(paste0("model.all",as.character(t + 1)), model.all)
  file <- paste0(path, "/data/temp/oa_rf/timeseries", as.character(t + 1), ".RData")
  save(model.all, file = file)
  rm(model.all)
}

@@

load(file = (paste0(path, "/data/temp/oa_rf/timeseries2001.RData")))

filenames <- list.files(paste0(path, "/data/temp/oa_rf"), pattern = "*.RData", full.names = T)

>>>>

library(tidyverse)
library(rprojroot)
#library(rgdal)
#library(rgeos)
library(sf)
library(spdep)
#library(tmap)
#library(maptools)
library(knitr)
library(REAT)
library(tidygeocoder)
library(geosphere)
library(broom)
#library(foreach)
library(doParallel)
library(raster)
library(plm)
#library(lmtest)
library(caret)
library(randomForest)
library(CAST)

@@

# out.path <- paste0(path, "/data/temp/for_oa_rf.RData")
# save.image(file = out.path)
# load(out.path)

@@

print(model.all)
# Random Forest 
# 
# 3716736 samples
#      10 predictor
# 
# No pre-processing
# Resampling: Cross-Validated (10 fold) 
# Summary of sample sizes: 2926910, 2926924, 3136005, 2926924, 3136005, 2926924, ... 
# Resampling results across tuning parameters:
# 
#   mtry  splitrule   RMSE      Rsquared   MAE      
#    2    variance    3.865809  0.5809699  0.5313035
#    2    extratrees  3.730542  0.6168954  0.5884731
#    6    variance    3.761356  0.6063340  0.5366004
#    6    extratrees  3.612670  0.6273041  0.5331196
#   10    variance    3.929176  0.5775066  0.5449132
#   10    extratrees  3.617598  0.6278302  0.5403551
# 
# Tuning parameter 'min.node.size' was held constant at a value of 5
# RMSE was used to select the optimal model using the smallest value.
# The final values used for the model were mtry = 6, splitrule =
#  extratrees and min.node.size = 5.

@@

path.out <- paste0(path, "/data/temp/oa_rf/all_OAs/all_OAs.RData")
save(model.all, file = path.out)

@@

#folds
k <- 3 # 7.09h for k=3

@@

detectCores()
cl <- makePSOCKcluster(2)
registerDoParallel(cl)

@@

regions <- df %>% distinct(RGN11CD)
regions <- as.vector(regions$RGN11CD)

@@

  set.seed(71)
  indices <- CreateSpacetimeFolds(df %>% filter(RGN11CD==i), 
                                spacevar = "oa11cd",
                                timevar = "year", 
                                k = k)

  # CV
  tc <- trainControl(method = "cv",
                   number = k,
                   seeds = seeds,
                   allowParallel = T,
                   index = indices$index,
                   savePredictions = 'final')

  model.all <- train(n ~ area + dist + dist.retail + London + south + 
                     n.slag + n.lag + n.l.slag + n.nearest.city + year,
                   data = df %>% filter(RGN11CD==i), 
                   trControl = tc,
                   method = "ranger",
                   na.action = na.omit,
                   #preProc = c("center", "scale"),
                   importance = "impurity")
  #assign(paste0("model.all",as.character(i)), model.all)

  file <- paste0(path, "/data/temp/oa_rf/regions/region_", as.character(i), ".RData")
  save(model.all, file = file)
  rm(model.all)
}

@@

```{r}
# create a list of the above model outputs
filenames <- list.files(paste0(path, "/data/temp/oa_rf/regions"), pattern = "*.RData", full.names = T)

for (i in filenames){
  load(file = i)
  i <- gsub("/home/nw19521/projects/web.diffusion/data/temp/oa_rf/regions/|.RData", "", i)
  assign(i, model.all)  
}

fit.model.all <- mget(ls(pattern = "^region_"))

# clear up
rm(model.all) # this is the last item from the loop
rm(list = ls(pattern = "^region_"))

@@

df.predictions <- data.frame()
for (i in regions){
  for (j in regions[!regions == i]){
    pred <- predict(fit.model.all[names(fit.model.all)==paste0("region_", i)], df[df$RGN11CD==j,])
    pred <- as.data.frame(pred)
    rownames(pred) <- c()
    assign(paste0("region.predict.model.", i, ".on.", j), pred)

    d <- paste0("region.predict.model.", i, ".on.", j)
    d <- cbind(get(d), df %>% filter(RGN11CD==j)) #%>% arrange(year, ladcd)
    d <- d[,c(5, 2, 4, 6, 1)]
    colnames(d)[5] <- "predictions"
    d <- d %>% mutate(trained.on = i)
    df.predictions <- rbind(d, df.predictions)
  }
}

df.predictions <- df.predictions %>% mutate(test.train = paste0(RGN11CD, ".", trained.on))

@@

  #assign(paste0("model.all",as.character(t + 1)), model.all)
  file <- paste0(path, "/data/temp/oa_rf/timeseries/timeseries", as.character(t + 1), ".RData")
  save(model.all, file = file)
  rm(model.all)
}

@@

#load(file = (paste0(path, "/data/temp/oa_rf/timeseries/timeseries2001.RData")))

filenames <- list.files(paste0(path, "/data/temp/oa_rf/timeseries/"), pattern = "*.RData", full.names = T)
